---
title: "FDA J-Comp Review-2 Prediction Models"
output: pdf_document
---

**Visualization**
```{r}
#Density Plot of CO2 over the dataset
library(lattice)
densityplot(df_train$co2, main = "Global Densilty of CO2")
```

```{r}
#Composition of Global CO2 share
library(ggplot2)
m1 <- mean(df_train$share_global_cement_co2)
m2 <- mean(df_train$share_global_coal_co2)
m3 <- mean(df_train$share_global_flaring_co2)
m4 <- mean(df_train$share_global_gas_co2)
m5 <- mean(df_train$share_global_oil_co2)

slices <- c(m1,m2,m3,m4,m5)
lbls <- c("Cement","Coal","Flaring","Gas","Oil")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls,pct)
lbls <- paste(lbls,"%",sep="")
pie(slices,labels=lbls,col=rainbow(length(lbls)),main="Pie Chart for Global Share of CO2 from Various Sources")
print(pie)
```

```{r}
#Visualization for China,United States,India
library(ggplot2)
China   = subset(df_train,country==5)
UnitedStates  = subset(df_train,country==18)
India  = subset(df_train,country==9)

#Population,GDP v/s Year
ggplot(China,aes(x=year)) + geom_line(aes(y=gdp),color="red") + geom_line(aes(y=population),color="blue")

ggplot(UnitedStates,aes(x=year)) + geom_line(aes(y=gdp),color="red") + geom_line(aes(y=population),color="blue")

ggplot(India,aes(x=year)) + geom_line(aes(y=gdp),color="red") + geom_line(aes(y=population),color="blue")

```

```{r}
library(graphics)
boxplot(China[,9:13],col="orange",border="black")
boxplot(UnitedStates[,9:13],col="blue",border="black")
boxplot(India[,9:13],col="green",border="black")
```

**Imputing NA Values with 0**
```{r}
df_train <- read.csv("Training_Dataset.csv")
df_test <- read.csv("Testing_Dataset.csv")

#Encoding datasets
df_train$country = factor(df_train$country,levels=c('Argentina','Australia','Bangladesh','Brazil','China','France','Germany','Hong Kong','India','Italy','Japan','Mexico','Portugal','Russia','South Africa','Turkey','United Kingdom','United States'),labels=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18))

df_test$country = factor(df_test$country,levels=c('Argentina','Australia','Bangladesh','Brazil','China','France','Germany','Hong Kong','India','Italy','Japan','Mexico','Portugal','Russia','South Africa','Turkey','United Kingdom','United States'),labels=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18))

#Imputing NA values with 0
df_train[is.na(df_train)] = 0
df_test[is.na(df_test)] = 0

#original values vector
orig <- c(df_test$share_global_co2)
library(caret)
```

<br>

**Model-1 : Multiple Linear Regression**
```{r}
print("1. Multiple Linear Regression")
regressor = lm(formula = share_global_co2 ~ .,
               data = df_train)
y_pred = predict(regressor, newdata = df_test)
pred <- c(y_pred)

#Measure of Accuracy
mae <- MAE(pred,orig)
rmse <- RMSE(pred,orig)
print(paste("Mean Absolute Error : ",mae))
print(paste("Root Mean Square Error : ",rmse))
summary(regressor)
```

<br>

**Model-2 : Support Vector Regression**
```{r}
library(e1071)
print("2. Support Vector Regression")
regressor = svm(formula = share_global_co2 ~ .,
                data = df_train,
                type = 'eps-regression',
                kernel = 'radial')
y_pred = predict(regressor, newdata = df_test)
pred <- c(y_pred)

#Measure of Accuracy
mae <- MAE(pred,orig)
rmse <- RMSE(pred,orig)
print(paste("Mean Absolute Error : ",mae))
print(paste("Root Mean Square Error : ",rmse))
```

<br>

**Model-3 : Decision Tree Regression**
```{r}
library(rpart)
print("3. Decision Tree Regression")
regressor = rpart(formula = share_global_co2 ~ .,
                  data = df_train,
                  control = rpart.control(minsplit = 1))
y_pred = predict(regressor, newdata = df_test)
pred <- c(y_pred)

#Measure of Accuracy
mae <- MAE(pred,orig)
rmse <- RMSE(pred,orig)
print(paste("Mean Absolute Error : ",mae))
print(paste("Root Mean Square Error : ",rmse))
```

<br>

**Model-4 : Random Forest Regression**
```{r}
print("4. Random Forest Regression")
library(randomForest)
set.seed(1234)
regressor = randomForest(x = df_train[,1:19],
                         y = df_train$share_global_co2,
                         ntree = 500)
y_pred = predict(regressor, newdata = df_test)
pred <- c(y_pred)

#Measure of Accuracy
mae <- MAE(pred,orig)
rmse <- RMSE(pred,orig)
print(paste("Mean Absolute Error : ",mae))
print(paste("Root Mean Square Error : ",rmse))
```
<br>


**Imputing NA Values with mean**
```{r}
df_train <- read.csv("Training_Dataset.csv")
df_test <- read.csv("Testing_Dataset.csv")

#Encoding datasets
df_train$country = factor(df_train$country,levels=c('Argentina','Australia','Bangladesh','Brazil','China','France','Germany','Hong Kong','India','Italy','Japan','Mexico','Portugal','Russia','South Africa','Turkey','United Kingdom','United States'),labels=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18))

df_test$country = factor(df_test$country,levels=c('Argentina','Australia','Bangladesh','Brazil','China','France','Germany','Hong Kong','India','Italy','Japan','Mexico','Portugal','Russia','South Africa','Turkey','United Kingdom','United States'),labels=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18))

#Imputing NA values with mean
for(i in 2:ncol(df_train)) {
  df_train[ , i][is.na(df_train[ , i])] <- mean(df_train[ , i], na.rm = TRUE)
}
for(i in 2:ncol(df_test)) {
  df_test[ , i][is.na(df_test[ , i])] <- mean(df_test[ , i], na.rm = TRUE)
}

#original values vector
orig <- c(df_test$share_global_co2)
library(caret)
```
<br>

**Model-1 : Multiple Linear Regression**
```{r}
print("1. Multiple Linear Regression")
regressor = lm(formula = share_global_co2 ~ .,
               data = df_train)
y_pred = predict(regressor, newdata = df_test)
pred <- c(y_pred)

#Measure of Accuracy
mae <- MAE(pred,orig)
rmse <- RMSE(pred,orig)
print(paste("Mean Absolute Error : ",mae))
print(paste("Root Mean Square Error : ",rmse))
summary(regressor)
```

<br>

**Model-2 : Support Vector Regression**
```{r}
library(e1071)
print("2. Support Vector Regression")
regressor = svm(formula = share_global_co2 ~ .,
                data = df_train,
                type = 'eps-regression',
                kernel = 'radial')
y_pred = predict(regressor, newdata = df_test)
pred <- c(y_pred)

#Measure of Accuracy
mae <- MAE(pred,orig)
rmse <- RMSE(pred,orig)
print(paste("Mean Absolute Error : ",mae))
print(paste("Root Mean Square Error : ",rmse))
```

<br>

**Model-3 : Decision Tree Regression**
```{r}
library(rpart)
print("3. Decision Tree Regression")
regressor = rpart(formula = share_global_co2 ~ .,
                  data = df_train,
                  control = rpart.control(minsplit = 1))
y_pred = predict(regressor, newdata = df_test)
pred <- c(y_pred)

#Measure of Accuracy
mae <- MAE(pred,orig)
rmse <- RMSE(pred,orig)
print(paste("Mean Absolute Error : ",mae))
print(paste("Root Mean Square Error : ",rmse))
```

<br>

**Model-4 : Random Forest Regression**
```{r}
print("4. Random Forest Regression")
library(randomForest)
set.seed(1234)
regressor = randomForest(x = df_train[,1:19],
                         y = df_train$share_global_co2,
                         ntree = 500)
y_pred = predict(regressor, newdata = df_test)
pred <- c(y_pred)

#Measure of Accuracy
mae <- MAE(pred,orig)
rmse <- RMSE(pred,orig)
print(paste("Mean Absolute Error : ",mae))
print(paste("Root Mean Square Error : ",rmse))
```

<br>

**Imputing NA Values with median**
```{r}
df_train <- read.csv("Training_Dataset.csv")
df_test <- read.csv("Testing_Dataset.csv")

#Encoding datasets
df_train$country = factor(df_train$country,levels=c('Argentina','Australia','Bangladesh','Brazil','China','France','Germany','Hong Kong','India','Italy','Japan','Mexico','Portugal','Russia','South Africa','Turkey','United Kingdom','United States'),labels=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18))

df_test$country = factor(df_test$country,levels=c('Argentina','Australia','Bangladesh','Brazil','China','France','Germany','Hong Kong','India','Italy','Japan','Mexico','Portugal','Russia','South Africa','Turkey','United Kingdom','United States'),labels=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18))

#Imputing NA values with median
for(i in 2:ncol(df_train)) {
  df_train[ , i][is.na(df_train[ , i])] <- median(df_train[ , i], na.rm = TRUE)
}
for(i in 2:ncol(df_test)) {
  df_test[ , i][is.na(df_test[ , i])] <- median(df_test[ , i], na.rm = TRUE)
}

#original values vector
orig <- c(df_test$share_global_co2)
library(caret)
```
<br>

**Model-1 : Multiple Linear Regression**
```{r}
print("1. Multiple Linear Regression")
regressor = lm(formula = share_global_co2 ~ .,
               data = df_train)
y_pred = predict(regressor, newdata = df_test)
pred <- c(y_pred)

#Measure of Accuracy
mae <- MAE(pred,orig)
rmse <- RMSE(pred,orig)
print(paste("Mean Absolute Error : ",mae))
print(paste("Root Mean Square Error : ",rmse))
summary(regressor)
```

<br>

**Model-2 : Support Vector Regression**
```{r}
library(e1071)
print("2. Support Vector Regression")
regressor = svm(formula = share_global_co2 ~ .,
                data = df_train,
                type = 'eps-regression',
                kernel = 'radial')
y_pred = predict(regressor, newdata = df_test)
pred <- c(y_pred)

#Measure of Accuracy
mae <- MAE(pred,orig)
rmse <- RMSE(pred,orig)
print(paste("Mean Absolute Error : ",mae))
print(paste("Root Mean Square Error : ",rmse))
```

<br>

**Model-3 : Decision Tree Regression**
```{r}
library(rpart)
print("3. Decision Tree Regression")
regressor = rpart(formula = share_global_co2 ~ .,
                  data = df_train,
                  control = rpart.control(minsplit = 1))
y_pred = predict(regressor, newdata = df_test)
pred <- c(y_pred)

#Measure of Accuracy
mae <- MAE(pred,orig)
rmse <- RMSE(pred,orig)
print(paste("Mean Absolute Error : ",mae))
print(paste("Root Mean Square Error : ",rmse))
```

<br>

**Model-4 : Random Forest Regression**
```{r}
print("4. Random Forest Regression")
library(randomForest)
set.seed(1234)
regressor = randomForest(x = df_train[,1:19],
                         y = df_train$share_global_co2,
                         ntree = 500)
y_pred = predict(regressor, newdata = df_test)
pred <- c(y_pred)

#Measure of Accuracy
mae <- MAE(pred,orig)
rmse <- RMSE(pred,orig)
print(paste("Mean Absolute Error : ",mae))
print(paste("Root Mean Square Error : ",rmse))
```
